Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-16 TEBenchmarkPaper/article.tex
Reference QuickSpec, HipSpec and Hipster

%IsaCoSy
The IsaCoSy system (Isabelle Conjecture Synthesis) conjectures equations by
enumerating expressions involving a given set of (typed) constants and free
variables (a signature). A constraint solver forbids certain (sub)expressions
from being synthesised, and these constraints are extended whenever a new
conjecture is generated, to avoid generating any special-cases of this
conjecture in the future. Conjectures are tested by sending them to the
QuickCheck counterexample finder and, if no counterexamples are found, then
sent to IsaPlanner which attempts to prove them.

%QuickSpec
QuickSpec emerged from work on the QuickCheck software testing framework for the
Haskell programming language, and has been used to generate conjectures for the
subsequent HipSpec and Hipster MTE systems. Like IsaCoSy, a signature is
provided and terms are enumerated. Rather than a constraint system, QuickSpec
version 1 collects expressions of the same type into equivalence classes,
assuming them to be equal. QuickCheck is used to test this assumption by
instantiating each variable with a randomly chosen value, evaluating the
resulting expressions and comparing them. Any equivalence class whose elements
don't compare equal are split up to separate those observably-different
expressions, and the process is repeated with new random values.

>>>>

%IsaCoSy
The IsaCoSy system (Isabelle Conjecture Synthesis) conjectures equations by
enumerating expressions involving a given set of (typed) constants and free
variables (a \emph{signature}). A constraint solver forbids certain
(sub)expressions from being synthesised, and these constraints are extended
whenever a new conjecture is generated, to avoid generating any special-cases of
this conjecture in the future. Conjectures are tested by looking for
counterexamples and, if none are found, sent to IsaPlanner which attempts to
prove them.

%QuickSpec
QuickSpec emerged from work on the QuickCheck software testing framework for the
Haskell programming language~\cite{claessen2011quickcheck}, and has been used to
generate conjectures for the subsequent
HipSpec~\cite{Claessen_hipspec:automating} and Hipster~\cite{Hipster} MTE
systems. Like IsaCoSy, a signature is provided and terms are enumerated. Rather
than a constraint system, QuickSpec version 1 collects expressions of the same
type into equivalence classes, assuming them to be equal. QuickCheck is used to
test this assumption by instantiating each variable with a randomly chosen
value, evaluating the resulting expressions and comparing them. Any equivalence
class whose elements don't compare equal are split up to separate those
observably-different expressions, and the process is repeated with new random
values.
